Internal models of type theory and internal higher categories for the Univalent Foundations

### 2014-07-01 article-models-ttinternal.tex
fixed the currying for weakening rule in section 3

\begin{lem}
Let $\cftalg{A}$ be a term-algebra in context $\Gamma$ and let
\begin{equation*}
\jhom
  {{{\Gamma}{\cftalgc{\cftalg{A}}}}{\cftalgf{\cftalg{A}}}}
  {\ctxwk{\cftalgf{\cftalg{A}}}{\cftalg{F_A}}}
  {\jcomp{}{\cftctxext}{\cftalg{F_A}}}
  {\cftwk{\cftalg{A}}}
\end{equation*}
be a homomorphism of term-algebras for which the diagram in
\autoref{diag:cftwk-cftwk} commutes judgmentally. Then
we have the judgmental equality
\begin{align*}
& \jcomp{}
  { \subst{q}{{{b}{{\gamma}{\cftctxext}}}{\cftwk{\cftalg{A}}}}
    }
  { \subst
      {{q}{{b}{\cftfamext}}}
      {{a}{{\gamma}{\boldsymbol{\mathcal{F}}_{\cftwk{\cftalg{A}}}}}}
    }
  \\
& \jdeq
  \jcomp{}
    { \subst{b}{{a}{{\gamma}{\boldsymbol{\mathcal{F}}_{\cftwk{\cftalg{A}}}}}}
      }
    { \subst
        { {q}{{b}{{a}{{\gamma}{\cftwkf{\cftalg{A}}}}}}}
        { {{{b}{{a}{{\gamma}{\cftwkc{\cftalg{A}}}}}}{{{a}{{\gamma}{\cftctxext}}}{\cftctxext}}}
          {\cftwk{\cftalg{A}}}
          }
      }
\end{align*}
of CFT-homomorphisms from $\subst{b}{{\gamma}{\cftalg{F_{F_A}}}}$ to
$ \subst
      { {q}{{b}{{a}{{\gamma}{\cftwkf{\cftalg{A}}}}}}
        }
      { {{b}{{a}{{\gamma}{\cftwkc{\cftalg{A}}}}}}
        {{a}{{\gamma}{\cftalg{F_{F_{F_{F_{A}}}}}}}}
        }$
in context $\Gamma$, for $\gamma:A$, $a,b:\subst{\gamma}{\cftalgf{\cftalg{A}}}$ and
$q:\subst{b}{{\gamma}{\cftalgf{\cftalg{F_A}}}}$.
\end{lem}

\subsubsection{Currying for weakening}
\begin{equation*}
\jhomeq
  { {{{\Gamma}{\cftalgc{\cftalg{A}}}}{\cftalgf{\cftalg{A}}}}
    {\cftalgf{\cftalg{F_A}}}
    }
  { \ctxwk
      {\cftalgf{\cftalg{F_A}}}
      {\cftalg{F_{F_A}}}
    }
  { \cftalg{F_{F_{F_A}}}
    }
  { \jcomp{}{\cftfamext}{\cftwk{\cftalg{A}}}
    }
  { \jcomp{}{\cftwk{\cftalg{A}}}{\jcomp{}{\cftctxext}{\cftwk{\cftalg{A}}}}
    }
\end{equation*}

>>>>

\begin{lem}
Let $\cftalg{A}$ be a CFT-algebra in context $\Gamma$ and let
\begin{equation*}
\jhom
  {{{\Gamma}{\cftalgc{\cftalg{A}}}}{\cftalgf{\cftalg{A}}}}
  {\ctxwk{\cftalgf{\cftalg{A}}}{\cftalg{F_A}}}
  {\jcomp{}{\cftctxext}{\cftalg{F_A}}}
  {\cftwk{\cftalg{A}}}
\end{equation*}
be a homomorphism of term-algebras for which the diagram in
\autoref{diag:cftwk-cftwk} commutes judgmentally. Then
we have the judgmental equality
\begin{align*}
& \jcomp{}
  { \subst{q}{{{b}{{\gamma}{\cftctxext}}}{\cftwk{\cftalg{A}}}}
    }
  { \subst
      {{q}{{b}{\cftfamext}}}
      {{a}{{\gamma}{\boldsymbol{\mathcal{F}}_{\cftwk{\cftalg{A}}}}}}
    }
  \\
& \jdeq
  \jcomp{}
    { \subst{b}{{a}{{\gamma}{\boldsymbol{\mathcal{F}}_{\cftwk{\cftalg{A}}}}}}
      }
    { \subst
        { {q}{{b}{{a}{{\gamma}{\cftwkf{\cftalg{A}}}}}}}
        { {{{b}{{a}{{\gamma}{\cftwkc{\cftalg{A}}}}}}{{{a}{{\gamma}{\cftctxext}}}{\cftctxext}}}
          {\cftwk{\cftalg{A}}}
          }
      }
\end{align*}
of CFT-homomorphisms from $\subst{b}{{\gamma}{\cftalg{F_{F_A}}}}$ to
$ \subst
      { {q}{{b}{{a}{{\gamma}{\cftwkf{\cftalg{A}}}}}}
        }
      { {{b}{{a}{{\gamma}{\cftwkc{\cftalg{A}}}}}}
        {{a}{{\gamma}{\cftalg{F_{F_{F_{F_{A}}}}}}}}
        }$
in context $\Gamma$, for $\gamma:A$, $a,b:\subst{\gamma}{\cftalgf{\cftalg{A}}}$ and
$q:\subst{b}{{\gamma}{\cftalgf{\cftalg{F_A}}}}$.
\end{lem}

\subsubsection{Currying for weakening}
\begin{equation}\label{eq:cftwk-currying}
\jhomeq
  { {{{\Gamma}{\cftalgc{\cftalg{A}}}}{\cftalgf{\cftalg{A}}}}
    {\cftalgf{\cftalg{F_A}}}
    }
  { \ctxwk
      {\ctxext{\cftalgf{\cftalg{A}}}{\cftalgf{\cftalg{F_A}}}}
      {\cftalg{F_A}}
    }
  { \cftalg{F_{F_{F_A}}}
    }
  { \jcomp{}{\cftfamext}{\cftwk{\cftalg{A}}}
    }
  { \jcomp{}{\ctxwk{\cftalgf{\cftalg{F_A}}}{\cftwk{\cftalg{A}}}}{\jcomp{}{\cftctxext}{\cftwk{\cftalg{A}}}}
    }
\end{equation}

\begin{lem}
Let $\cftalg{A}$ be a CFT-algebra in context gamma with a CFT-homomorphism 
$ \jhom
  {{{\Gamma}{\cftalgc{\cftalg{A}}}}{\cftalgf{\cftalg{A}}}}
  {\ctxwk{\cftalgf{\cftalg{A}}}{\cftalg{F_A}}}
  {\jcomp{}{\cftctxext}{\cftalg{F_A}}}
  {\cftwk{\cftalg{A}}}
$
satisfying the judgmental equality of \autoref{eq:cftwk-currying}. Then we
have the judgmental equality
\begin{equation*}
\subst{{p}{{a}{\cftfamext}}}{{\gamma}{\cftwk{\cftalg{A}}}}
\jdeq
\jcomp{}
    {\subst{a}{{\gamma}{\cftwk{\cftalg{A}}}}}
    {\subst{p}{{{a}{{\gamma}{\cftctxext}}}{\cftwk{\cftalg{A}}}}}
\end{equation*}
of CFT-homomorphisms from $\subst{\gamma}{\cftalg{F_A}}$ to 
$\subst{p}{{a}{{\gamma}{\cftalg{F_{F_{F_A}}}}}}$ in context $\Gamma$,
for every $\gamma:A$, $a:\subst{\gamma}{\cftalgf{\cftalg{A}}}$ and
$p:\subst{a}{{\gamma}{\cftalgf{\cftalg{F_A}}}}$. 
\end{lem}
